Performance of Rookie Can Predict Price of Their Rookie Prizm Silver Cards

### 2024-04-24 paper/paper.qmd
updated mock data for model

I will create a test data set for 2024-2025 and 2026-2027 season and use the model with this test data set to predict the price of these players using their own model. In @tbl-5, @tbl-6, and @tbl-7 are the predicted data based by improving the players statistics slightly.

@@

test_maxey <- tibble(
  REB = c(
    4.5, 4.3, 5.1, 3.1, 4.5, 5.6, 7.8, 4.5, 6.5, 4.1, 4.3, 6.5, 5.8, 5.5
  ),
  AST = c(
    4.5, 4.3, 5.1, 3.1, 4.5, 5.6, 7.8, 4.5, 6.5, 4.1, 4.3, 6.5, 5.8, 5.5
  ),
  BLK = c(
    4.5, 4.3, 5.1, 3.1, 4.5, 5.6, 7.8, 4.5, 6.5, 4.1, 4.3, 6.5, 5.8, 5.5
  ),
  STL = c(
    4.5, 4.3, 5.1, 3.1, 4.5, 5.6, 7.8, 4.5, 6.5, 4.1, 4.3, 6.5, 5.8, 5.5
  ),
  PTS = c(
    20, 25, 40, 30, 45, 20, 30, 35, 20, 15, 35, 30, 35, 20 
  )
)

maxey_prediction <- predict(maxey_model, newdata = test_maxey)

@@

test_haliburton <- tibble(
  REB = c(
    4.5, 4.3, 5.1, 3.1, 4.5, 5.6, 7.8, 4.5, 6.5, 4.1, 4.3, 6.5, 5.8, 5.5
  ),
  AST = c(
    4.5, 4.3, 5.1, 3.1, 4.5, 5.6, 7.8, 4.5, 6.5, 4.1, 4.3, 6.5, 5.8, 5.5
  ),
  BLK = c(
    4.5, 4.3, 5.1, 3.1, 4.5, 2.6, 3.8, 4.5, 2.5, 4.1, 4.3, 4.5, 5.8, 5.5
  ),
  STL = c(
    4.5, 4.3, 2.1, 3.1, 4.5, 2.6, 4.8, 4.5, 6.5, 4.1, 4.3, 4.5, 2.8, 4.5
  ),
  PTS = c(
    20, 25, 10, 30, 25, 20, 30, 35, 20, 15, 35, 30, 35, 20 
  )
)

haliburton_prediction <- predict(haliburton_model, newdata = test_haliburton)

@@

test_anthony <- tibble(
  REB = c(
    4.5, 4.3, 5.1, 3.1, 4.5, 5.6, 7.8, 4.5, 6.5, 4.1, 4.3, 6.5, 5.8, 5.5
  ),
  AST = c(
    4.5, 4.3, 5.1, 3.1, 4.5, 5.6, 7.8, 4.5, 6.5, 4.1, 4.3, 6.5, 5.8, 5.5
  ),
  BLK = c(
    4.5, 4.3, 5.1, 3.1, 4.5, 2.6, 3.8, 4.5, 2.5, 4.1, 4.3, 4.5, 5.8, 5.5
  ),
  STL = c(
    4.5, 4.3, 2.1, 3.1, 4.5, 2.6, 4.8, 4.5, 6.5, 4.1, 4.3, 4.5, 2.8, 4.5
  ),
  PTS = c(
    20, 25, 10, 30, 25, 20, 30, 35, 20, 15, 35, 30, 35, 20 
  )
)

anthony_prediction <- predict(anthony_model, newdata = test_anthony)

@@

view(anthony_prediction_table)
```

@@

## Average player statistics

>>>>

I will create a test data set for 2024-2025 and 2026-2027 season and use the model with this test data set to predict the price of these players using their own model. In @tbl-5, @tbl-6, and @tbl-7 are the predicted data based by improving the players statistics slightly. The mock data wick use the original data from 2022 to 2024 with an increase of 2% each month to see if increasing performance statistics have an impact on the card price.

@@

test_maxey_price_only <- clean_maxey[, -1]

test_maxey_price_only[1, ] <- (test_maxey_price_only[1, ])*1.02
test_maxey_price_only[2, ] <- (test_maxey_price_only[2, ])*1.04
test_maxey_price_only[3, ] <- (test_maxey_price_only[3, ])*1.06
test_maxey_price_only[4, ] <- (test_maxey_price_only[4, ])*1.08
test_maxey_price_only[5, ] <- (test_maxey_price_only[5, ])*1.10
test_maxey_price_only[6, ] <- (test_maxey_price_only[6, ])*1.12
test_maxey_price_only[7, ] <- (test_maxey_price_only[7, ])*1.14
test_maxey_price_only[8, ] <- (test_maxey_price_only[8, ])*1.16
test_maxey_price_only[9, ] <- (test_maxey_price_only[9, ])*1.18
test_maxey_price_only[10, ] <- (test_maxey_price_only[10, ])*1.20
test_maxey_price_only[11, ] <- (test_maxey_price_only[1, ])*1.22
test_maxey_price_only[12, ] <- (test_maxey_price_only[12, ])*1.24
test_maxey_price_only[13, ] <- (test_maxey_price_only[13, ])*1.26
test_maxey_price_only[14, ] <- (test_maxey_price_only[14, ])*1.28

maxey_prediction <- predict(maxey_model, newdata = test_maxey_price_only)

@@

test_haliburton_price_only <- clean_haliburton[, -1]

test_haliburton_price_only[1, ] <- (test_haliburton_price_only[1, ])*1.02
test_haliburton_price_only[2, ] <- (test_haliburton_price_only[2, ])*1.04
test_haliburton_price_only[3, ] <- (test_haliburton_price_only[3, ])*1.06
test_haliburton_price_only[4, ] <- (test_haliburton_price_only[4, ])*1.08
test_haliburton_price_only[5, ] <- (test_haliburton_price_only[5, ])*1.10
test_haliburton_price_only[6, ] <- (test_haliburton_price_only[6, ])*1.12
test_haliburton_price_only[7, ] <- (test_haliburton_price_only[7, ])*1.14
test_haliburton_price_only[8, ] <- (test_haliburton_price_only[8, ])*1.16
test_haliburton_price_only[9, ] <- (test_haliburton_price_only[9, ])*1.18
test_haliburton_price_only[10, ] <- (test_haliburton_price_only[10, ])*1.20
test_haliburton_price_only[11, ] <- (test_haliburton_price_only[1, ])*1.22
test_haliburton_price_only[12, ] <- (test_haliburton_price_only[12, ])*1.24
test_haliburton_price_only[13, ] <- (test_haliburton_price_only[13, ])*1.26
test_haliburton_price_only[14, ] <- (test_haliburton_price_only[14, ])*1.28

haliburton_prediction <- predict(haliburton_model, newdata = test_haliburton_price_only)

@@

test_anthony_price_only <- clean_anthony_edward[, -1]

test_anthony_price_only[1, ] <- (test_anthony_price_only[1, ])*1.02
test_anthony_price_only[2, ] <- (test_anthony_price_only[2, ])*1.04
test_anthony_price_only[3, ] <- (test_anthony_price_only[3, ])*1.06
test_anthony_price_only[4, ] <- (test_anthony_price_only[4, ])*1.08
test_anthony_price_only[5, ] <- (test_anthony_price_only[5, ])*1.10
test_anthony_price_only[6, ] <- (test_anthony_price_only[6, ])*1.12
test_anthony_price_only[7, ] <- (test_anthony_price_only[7, ])*1.14
test_anthony_price_only[8, ] <- (test_anthony_price_only[8, ])*1.16
test_anthony_price_only[9, ] <- (test_anthony_price_only[9, ])*1.18
test_anthony_price_only[10, ] <- (test_anthony_price_only[10, ])*1.20
test_anthony_price_only[11, ] <- (test_anthony_price_only[1, ])*1.22
test_anthony_price_only[12, ] <- (test_anthony_price_only[12, ])*1.24
test_anthony_price_only[13, ] <- (test_anthony_price_only[13, ])*1.26
test_anthony_price_only[14, ] <- (test_anthony_price_only[14, ])*1.28

anthony_prediction <- predict(anthony_model, newdata = test_anthony_price_only)

@@

@@

## Price of increasing performance
